Paper Notes

### 2019-12-03 paper_notes.tex
Add paper_note2

There are two kinds of identification problems. 
1. One is to identify the treatment effect, a typical example is the selection bias. The problem in these cases are that selection (determing who is treated or observed) and outcomes may be correlated. 
2. Another is to identify the true coefficient in a linear regression when regressors are measureed with error.

@@

>>>>

There are two kinds of identification problems. 
1. One is to identify the treatment effect, a typical example is the selection bias. The problem in these cases are that selection (determing who is treated or observed) and outcomes may be correlated. 
2. Another is to identify the true coefficient in a linear regression when regressors are measured with error.

@@

\part{Education} % (fold)
\label{prt:education_}

\chapter{Charter School} % (fold)
\label{sec:charter_school}

\section{Singleton, 2019 AER} % (fold)
\label{sec:singleton_2019_aer}

\textbf{\bibentry{Singleton:2019uy}}

This paper investigates the following questions:
\begin{enumerate}
	\item How the non-differentiated stipend will affect the entry decision of charter schools, and then further affect the admission diversity of students?
	\item Once a charter school is established, it cannot screen students. But it can pre-screen students by choosing where to locate. Different locations have very different student compositions.
\end{enumerate}

% section singleton_2019_aer (end)

% section charter_school (end)

% part education_ (end)
